Stability of variational quantum dynamics with Gaussian approximants

### 2013-08-06 paper.tex
writing

>>>>

However, in these single mode numerical experiments, it is often useful to expand over a regular grid.  For example, this allows us to plot phase space functions.  It is convenient to normalise the samples so that $‖\vec g‖=‖A\vec g‖$.  If the sample amplitudes $α_r$ form a square gird with spacing $h$, the condition $\vec g_r=cg(α_r)$ is satisfied when
$$∑_r|\vec g_r|²=c²∑_r|g(α_r)|²=\int |g|²\,d²α≈h²∑_r|g(α_r)|²,$$
whence $c=h$, and the discretisation is
$$\vec g_r=hg(α_r).$$
